--- 
title: "Airbnb in New York City"
author: "Jing You, Annai Wang, Sijie Cai, Jinyan Lyu"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
---
```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```

# Introduction


<!--chapter:end:index.Rmd-->

```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```
# Data Sources

The data we use for this project is the newest listings Airbnb data for New York City, which is obtained directly from the Inside Airbnb website : http://data.insideairbnb.com/united-states/ny/new-york-city/2020-10-05/data/listings.csv.gz. New York City has always been one of the hottest markets for Airbnb. We believe targeting NYC dataset would provide us rich information to understand the rental landscape in NYC. Note that in this project we only use the listings data. Although Reviews data and Calendar data for upcoming year is also available on the website, we would like to focus on the unbiased numerical data that has been validated. 


The listings dataset is consists of 74 attributes for 44,666 listing in New York City. As we aim to gain a holistic analysis of the Aribnb market in New York City, we discard many uninformative or miscellaneous attributes such as id, host names, urls, review times, and descriptions etc. We deliberately select 18 attributes that covers the The attributes we selected for our analysis are the following: 

*   Listing id : contiunous variable, the id of the listing

*   Host id : contiunous variable, the id of the host of the listing

*   Host_is_superhost : categorical variable, whether or not the host for this listing is superhost (Experienced hosts who provide a shining example for other hosts, and extraordinary experiences for their guests)

*   Neighbourhood_cleansed : categorical variable, the neighborhood of the listing (Midtown, Hell's Kitchen, Upper West Side ...)

*   Neighborhood_group_cleansed : categorical variable, the neighborhood group of the listing (Manhatten, Brooklyn, Bronx ...)

*   Latitude : contiunous variable, the latitude of the listing

*   Longitude : contiunous variable, the longtitude of the listing

*   Room_type : categorical variable, the room type of the listing (Entire home, Private room ...)

*   Bedrooms : categorical variable, the number of bedrooms in the listing

*   Price : contiunous variable, the price per night for the listing

*   Reviews per month : contiunous variable, the average number of reviews the listing received per month

*   Review_scores_rating : contiunous variable, the overall rating of the listing

*   Review_scores_location : contiunous variable, the rating for the locating of the listing

*   Availability_365 : contiunous variable, the number of available days of the listing per year


We notice several issues related to the dataset:

* Missing values : There are NA's in 4 columns (bedrooms, reviews_per_month, reviews_scores_rating, review_scores_location)

* Non-Availability : Almost half of the listings has 0 available days for booking in the year. Note that the host has the choice to set their listing as not available. 

The datailed treatment of those issues will be discussed in the following chapters. 





```{r, include=FALSE}
library(dplyr)
listings <- read.csv(file = "data/listings.csv") %>% select(id,host_id, host_is_superhost, neighbourhood_cleansed, neighbourhood_group_cleansed, latitude, longitude, room_type, bedrooms, price, reviews_per_month, review_scores_rating, review_scores_location, availability_365)
summary(listings)
```

<!--chapter:end:02-data.Rmd-->

```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```
# Data transformation

The listings dataset is in csv format, which can be loaded into R directly. Although we import the data successfully, there are some transformations needed in order to perform further analysis. 

1. Subset the data. We reduced the dataset from 76 attributes to our selected 18 attributes. 

```{r, include=FALSE}
library(dplyr)
listings <- read_csv("Data/listings.csv.zip") %>% select(id,host_id, host_is_superhost, neighbourhood_cleansed, neighbourhood_group_cleansed, latitude, longitude, room_type, bedrooms, price, reviews_per_month, review_scores_rating, review_scores_location, availability_365)
```

2. Missing values. We observe that there are no 0s in the "bedrooms" attribute. After exploring the listings description in the dataset and the Airbnb website, we notice that studios listing does not specify bedroom number. Therefore those listings with N/A bedrooms are all studios. In order to differentiate studio from other one-bedroom listings, we decided to use 0 bedrooms to denote those studios. 

```{r, include=FALSE}
listings$bedrooms[is.na(listings$bedrooms)] <-0
```


3. Encode categorical variables. We encode the categorical variables neibourhood, neibourhood_group, room_type, and bedrooms as factors with corresponding levels. Note that we aggregate all bedrooms number greater than 4 as ">4" since those are rare conditions. 

```{r, echo=FALSE,warning=FALSE}
listings <- listings %>%
  mutate(neibourhood_cleansed = as.factor(neighbourhood_cleansed)) %>%
  mutate(neibourhood_group_cleansed = as.factor(neighbourhood_group_cleansed)) %>%
  mutate(room_type, as.factor(room_type)) %>%
  mutate(bedrooms = fct_collapse(factor(bedrooms),"0" = "0", "1" = "1","2" = "2","3" = "3","4" = "4",group_other = TRUE))%>%
  mutate(bedrooms = fct_collapse(bedrooms, "0" = "0","1" = "1","2" = "2", "3" = "3","4" = "4",">4" = "Other")) 
```

4. Rename variables. We rename the variables name to be more reflective of the cotents. 

```{r, echo=FALSE,warning=FALSE}
listings <- listings %>%
  rename(
    neibourhood= neibourhood_cleansed,
    neighbourhood_group = neighbourhood_group_cleansed,
    rating = review_scores_rating,
    rating_location = review_scores_location,
    year_availability = availability_365,
  )
```

<!--chapter:end:03-cleaning.Rmd-->

```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```
# Missing values

The listings dataset has missing values in the following columns : review_scores_location, review_scores_rating, reviews_per_month, bedrooms. 


```{r, include=FALSE}
library(dplyr)
library(tidyverse)
listings <- read_csv("Data/listings.csv.zip") %>% select(id,host_id, host_is_superhost, neighbourhood_cleansed, neighbourhood_group_cleansed, latitude, longitude, room_type, bedrooms, price, reviews_per_month, review_scores_rating, review_scores_location, availability_365)
```


```{r, echo=FALSE}
library(naniar)
gg_miss_var(listings) + labs(title = 'Number of missing points in Airbnb listings Data')
```

```{r, echo=FALSE,warning=FALSE}
 
```


As for missing values in "bedrooms", we observe that there are no 0s in the "bedrooms" attribute. After exploring the listings description in the dataset and the Airbnb website, we notice that studios listing does not specify bedroom number.  

```{r, echo=FALSE,warning=FALSE}
library(ggplot2)
ggplot(listings, aes(as.factor(bedrooms))) +
geom_bar(color = "grey50", fill = "lightblue",xlab="Number of bedrooms") 
```

<!--chapter:end:04-missing.Rmd-->

```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```
# Results

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r cars}
library(readr)
data <- read_csv("/Users/lvjinyan/Desktop/listings.csv")
dataset<-read_csv("/Users/lvjinyan/Desktop/listings.csv")
str(data)
library(tidyverse)
library(ggplot2)
library(GGally)
library(ggalluvial)
library(parcoords)
```



```{r}
#numerical
#histgram of price
ggplot(data=data, aes(price))+
  geom_histogram(fill='plum4',color='plum')+
  labs(x='price')+
  ggtitle('Histogram of all price')
  
ggplot(data=data, aes(price))+
  geom_histogram(binwidth=10,fill='plum4',alpha=0.75)+
  scale_x_continuous(name="price", limits=c(0, 1500))+
  labs(x='price')+
  ggtitle('Histogram of price from 0 to 1500')
#
```
There exist a significant outlier in 10000, so we scale our x aixs from 0 to 1500.
In our new histogram, we could conduct that there is a trend that most host would like to give a integer price with 0 in ones/ unit digit, and also 0 in tenth digit. 

```{r}
#histgram of rating
ggplot(data=data, aes(rating))+
  geom_histogram(fill='plum4',alpha=0.75)+
  labs(x='Rating')+
  ggtitle('Histogram of all Rating')
```
From the rating plot, most the rating score concentrated on (75,100), and people trend to give 100 as the default score. Otherwise, the score will be super low less than 60. It show the rating score are subjective to personal emotion. And also, select bias effect the rating score, once people choose give the listing housing a review, they either extremely love or hate this house. 




```{r}
#boxplot
ggplot(data, aes(x = reorder(neighbourhood_group, -price, median), y = price)) + 
  geom_boxplot(fill = "green4",alpha=0.5)+
  scale_y_continuous(name="price", limits=c(0, 500))+
  labs(x='Neighbourhood Group')+
  ggtitle('The Boxplot of Five Neighbourhood Group with ordered by price median')
```

The box plot of five neighbourhood and rank by the median of prices shows Manhattan has the highest median price. And the Bron has the lowest median price. Even though the median price in five neighbourhoods are relative simliar. In addition, there is a hugh amount of outliers in the higher price. Even if there are a wider range outlier, the majority price still lower than $400.


```{r}
dataset$host_since <- format(as.Date(dataset$host_since),
                             "%Y%m%d")
dataset$host_since <- as.Date(dataset$host_since, 
                              tryFormats = "%Y%m%d")
df1 <- dataset %>%
  filter(price<1500 & host_since<="2021-01-01" & host_since>="2010-01-01") 
ggplot(df1,aes(host_since,price))+
  geom_line(col="lightblue")+
  labs(x="Date",y="Price")+
  ggtitle("Time Series of Price on Year for Airbnb in NYC")
df2 <- dataset %>%
  filter(price<1500 & host_since<"2020-01-01" & host_since>="2019-01-01")
ggplot(df2,aes(host_since,price))+
  geom_line(col="orange")+
  labs(x="Date",y="Price")+
  ggtitle("Time Series of Price on Year 2019 for Airbnb in NYC")
df4 <- dataset %>%
  filter(price<1500 & host_since<"2018-01-01" & host_since>="2017-01-01")
ggplot(df4,aes(host_since,price))+
  geom_line(col="pink1")+
  labs(x="Date",y="Price")+
  ggtitle("Time Series of Price on Year 2017 for Airbnb in NYC")
df3 <- dataset %>%
  filter(price<1500 & host_since<"2021-01-01" & host_since>="2020-01-01")
ggplot(df3,aes(host_since,price))+
  geom_line(col="skyblue3")+
  labs(x="Date",y="Price")+
  ggtitle("Time Series of Price on Year 2020 for Airbnb in NYC")
```

First, we adjust the price since we consider extreme price points as outliers. We filter the dataset when price is less than 1300 dollars. Then we draw time series plots to see if there is any obvious pattern for date and price, which means we would like to explore if price is significantly associately with seasons.
From the first plot, it is hard for us to see any patterns. What we can observe is that most of prices are clustered below 500 dollars. Then we zoom in the data a little bit to see if there is any changes. The second and third time series plot is for year 2017 and 2019 seperatly, it is also hard to tell seasonal trend exits from both plots. And two plots look pretty similar. However, we can say that the frequencies of high prices are commonly seen in summer and winter, which is kind of consistent with summer vacation and winter holiday. Therefore, we could conclude price will be higher than usual especially in summer/winter holidays when people are more likely to travel during those time periods. 
Then we would like to know how the covid19 pandemic will affect Airbnb, so we draw another time series plot for year 2020. Based on the plot, we observe some differences between year 2020 and other years. First, we know the overall price is much lower than usual. Second, after April, the number of booking is jumped down so obviously, which is consistent with the situation of the pandemic.

```{r}
dataset <- dataset %>%
  na.omit() %>%
  mutate(rating_rank=case_when(rating==100 ~ "Perfect",
                               rating>=95 & rating<100 ~ "Very Good",
                               rating>=90 & rating<95 ~ "Good",
                               rating>=80 & rating<90 ~ "Fair",
                               rating<80 ~ "Bad"
                               ))
c1 <- c("coral","plum1","skyblue1","orange")
vcd::mosaic(room_type~neighbourhood_group,
            highlighting_fill=c1,
            dataset)
c2 <- c("lightblue","orangered")
vcd::mosaic(host_is_superhost~neighbourhood_group,
            highlighting_fill=c2,
            dataset)
c3 <- c("skyblue3","salmon")
vcd::mosaic(host_is_superhost~rating_rank,
            highlighting_fill=c3,
            dataset)
```

We applied mosaic plots to see frequencies for five areas based on room type and superhost, seperately. From the first plot, we can observe that entire home/apt and private room take the majority part of the room types in NYC Airbnb, which makes sense since few guests would like to share room/space with strangers. Also, it makes hosts' lives much easier if they own the entire house/apt when they join the Airbnb, since they do not need to have aggrements with their roommates.
The second plot shows that non-superhost is the majority among hosts in different areas in NYC.
Also, we would like to find whether there is a positive relationship between superhost and rating, which implies superhost is more likely to get a better rating score for living experience. From the last plot, it is not obvious for us to confirm that hypothsis, however, we observe a bunch of guests have great living experience, regardless of superhost or not.



```{r}
#cleveland Dot Plot
data%>%group_by(neighbourhood_group,rating_location)%>%summarise(count=n())%>%na.omit()%>%mutate(ave=mean(rating_location))%>%select(neighbourhood_group,ave)%>%
  ggplot(aes(x= ave,y=reorder(neighbourhood_group, ave)))+
  geom_point(color='blue')+
  labs(x='Average rating score',y='Neighbourhood')+
  ggtitle(' Neighbourhood average rating score')
data%>%filter(neighbourhood_group=='Brooklyn')%>%group_by(neighbourhood,rating_location)%>%summarise(count=n())%>%na.omit()%>%mutate(ave=mean(rating_location))%>%select(neighbourhood,ave)%>%
  ggplot(aes(x= ave,y=reorder(neighbourhood, ave)))+
  geom_point(color='blue')+
  labs(x='Brooklyn average rating score',y='Brooklyn Neighbourhood')+
  ggtitle('Brooklyn Neighbourhood average rating score')
data%>%filter(neighbourhood_group=='Bronx')%>%group_by(neighbourhood,rating_location)%>%summarise(count=n())%>%na.omit()%>%mutate(ave=mean(rating_location))%>%select(neighbourhood,ave)%>%
  ggplot(aes(x= ave,y=reorder(neighbourhood, ave)))+
  geom_point(color='blue')+
  labs(x='Bronx average rating score',y='Bronx Neighbourhood')+
  ggtitle('Bronx Neighbourhood average rating score')
data%>%filter(neighbourhood_group=='Manhattan')%>%group_by(neighbourhood,rating_location)%>%summarise(count=n())%>%na.omit()%>%mutate(ave=mean(rating_location))%>%select(neighbourhood,ave)%>%
  ggplot(aes(x= ave,y=reorder(neighbourhood, ave)))+
  geom_point(color='blue')+
  labs(x='Manhattan average rating score',y='Manhattan Neighbourhood')+
  ggtitle('Manhattan Neighbourhood average rating score')
data%>%filter(neighbourhood_group=='Queens')%>%group_by(neighbourhood,rating_location)%>%summarise(count=n())%>%na.omit()%>%mutate(ave=mean(rating_location))%>%select(neighbourhood,ave)%>%
  ggplot(aes(x= ave,y=reorder(neighbourhood, ave)))+
  geom_point(color='blue')+
  labs(x='Queens average rating score',y='Queens Neighbourhood')+
  ggtitle('Queens Neighbourhood average rating score')
data%>%filter(neighbourhood_group=='Staten Island')%>%group_by(neighbourhood,rating_location)%>%summarise(count=n())%>%na.omit()%>%mutate(ave=mean(rating_location))%>%select(neighbourhood,ave)%>%
  ggplot(aes(x= ave,y=reorder(neighbourhood, ave)))+
  geom_point(color='blue')+
  labs(x='Staten Island average rating score',y='Staten Island Neighbourhood')+
  ggtitle('Staten Island Neighbourhood average rating score')
```



the cleveland dot plot of five neighbourhoods, we could see the average rating score of Staten Island is the highest, while Brooklyn is the lowest rating score. Besides, the average rating score of all neighbourhood group are apporomately simliar the highst is 7 and lowest is 6.

In Brooklyn, Bushwick has the lowest average rating score about 6, while Navy Yard, Fort Hamilton, and Brooklyn Heights, are the three neighbourhood touristor thought they are perfect with grade 10. Besides, most neighbourhoods in Brooklyn gets a score from 7 to 9.

In Bronx, the score range are relatively wider, which means people may be polarization. West Farm has the lowest average rating score about 5.5, compare with Castle Hill has the highest rating score in 10 as perfect. The average rating score of all neighbourhood group in Bronx are from 8.3 to 9.5.

In Manhattan, NoHo and Maple Hill has the highest rating score. And those central business district and shopping center like Midtown has the relatively lower rating score. And we can see the Upper town west where Columbia located also has the relatively low rating score. In addition, Harlem and East Harlem have the lowest score around 6.33.

In Queens, Rego Park has the lowest score like 6.2, and about 6 neighbourhood has the highest rating score.

In Staten Island, the range of score are narrower than others, which means people recommend most neighbourhood in Staten Island. Tompkinsville has the lowest rating score about 7.1. Other neighbouhood in Staten Island have a score higher than 8. And most of them are either 9.5 or 10. Staten Island might be most recommend living place for tourist. 





```{r}
ggparcoord(dataset, columns=c(10,12,20,22),
           alphaLines = 0.3,
           scale="uniminmax",
           groupColumn=9, 
           title = "Parallel Coordinate Plot Based on Room Types")
ggparcoord(dataset, 
           columns=c(10,12,20,22),
           alphaLines = 0.3,
           scale="uniminmax",
           groupColumn=23, 
           title = "Parallel Coordinate Plot Based on Rating Ranks")
```

We use parallel coordinate plots to explore if any relationships exist among those numeric variables, such as number of bedrooms, price. Also,we draw those plots based on levels of selected categorical variables, such as rating_rank, room_type.
The first plot is grouped by room_type. From the plot, we see entire home/apt and private room have a majority part among all types. We observe there is a negative relationship between number of bedrooms and price, which makes more sense if we consider room types here. It is obvious to see there is a positive relationship between price and rating. If price is high, the quality of the house is great, on average, thus guests will have good living experience. What's more, there is a negative relationship between rating and reviews_per_month.
The second plot is based on rating_rank. The shape of the plot is pretty similar with the one in the first plot. Negative relationships between number of bedrooms and price, rating and reviews_per_month. And a positive relationship between price and rating.

```{r}
ggplot(as.data.frame(count(dataset, 
                           host_is_superhost,
                           rating_rank,
                           neighbourhood_group,
                           room_type)),
        aes(y=n, axis=host_is_superhost, 
            axis1=room_type, 
            axis2=neighbourhood_group, 
            axis3=rating_rank))+
  geom_alluvium(aes(fill=host_is_superhost))+
  geom_stratum(width=1/12, 
               fill='lightgrey',
               color='grey')+
  geom_label(stat = "stratum", 
             aes(label = after_stat(stratum))) + 
        scale_fill_brewer(type = "qual", 
                          palette = "Set1") +  
        ggtitle('Alluvial Plot Colored by Superhost') +  
        theme_void()
```

From the alluvial plot, we clearly see that super-host is a small part among hosts in NYC Airbnb since a bunch of flows go through the FALSE node. For room types, entire home/apt and private room take the majority part among all types, which is consistent with travelers' preference. Also, we observe that most Airbnb housing is located in Manhattan, which implies travelers will consider Manhattan first and it has a priority over other areas in NYC. In addition, guests have great living experience on average since most guests give the housing very good score. From the plot, we see a lot of flows pass through ranking nodes: Good, Very Good and Perfect. Also, super-hosts tend to have higher ratings since we barely see blue flows via Fair and Bad nodes. In general, Airbnb housing in NYC provides guests/travelers great living experiences.



<!--chapter:end:05-results.Rmd-->

```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```
# Interactive component



<!--chapter:end:06-interactive.Rmd-->

```{r include=FALSE, cache=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```
# Conclusion


<!--chapter:end:07-conclusion.Rmd-->

